---
title: "Programs"
author: "Lars Vilhuber"
date: "May 22, 2018"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Program directory
This directory contains all programs necessary to run the cleaning, analysis, etc. They can be run separately, or from the master document (paper). 

## Setup
Most parameters are set in the `config.R`:
```{r setup_config}
source(file.path(rprojroot::find_rstudio_root_file(),"pathconfig.R"),echo=TRUE)
source(file.path(programs,"config.R"), echo=TRUE)
```

Any libraries needed are called and if necessary installed through `libraries.R`:

```{r setup_libraries}
source(file.path(basepath,"global-libraries.R"),echo=TRUE)
source(file.path(programs,"libraries.R"), echo=TRUE)
```



## Download the replication data from Google Sheet
The responses to the replication attempts are stored on Google Sheets. 
```{r download_replication,eval=FALSE}
source(file.path(programs,"01_download_replication.R"),echo=TRUE)
```

## Get CrossRef information
The master replication list has all the DOIs. We clean that up first, and then  look up the DOI at CrossRef.
```{r read_clean_list,cache=TRUE}
source(file.path(programs,"02_read_clean_replicationlist.R"),echo=TRUE)
```

```{r get_crossref,cache=TRUE,eval=FALSE}
source(file.path(programs,"03_get_crossref.R"),echo=TRUE)
```

```{r clean_replication,cache=TRUE}
source(file.path(programs,"04_clean_replicationlist.R"),echo=TRUE)
```





## Core analysis and figures
We can now tabulate the replications listed (not run) by journal and year:
```{r list_journals,results='asis'}
repllist4 <- readRDS(file=file.path(interwrk,"replication_list_clean.Rds"))
entryQ <- readRDS(file = file.path(dataloc,"entryQ.Rds"))
table1 <- repllist4 %>% 
	merge(entryQ,by="DOI") %>%
	group_by(journal,year) %>% filter(!is.na(journal)) %>% summarize(n=n()) %>% spread(year,n) %>%
	ungroup() %>%
	mutate(Total = rowSums(select(.,-journal),na.rm = TRUE)) 
write.csv(table1,file.path(TexIncludes,"journal_by_year.csv"),quote = FALSE,row.names = FALSE,na = "")
knitr::kable(table1)
```
We also tabulate the replication results. Note that this is a noisy measure: in some cases, when only an assessment was made, replication was set to "no", which is incorrect.

```{r list_journals2,results='asis'}

table2 <- repllist4 %>% 
	merge(entryQ,by="DOI") %>% 
	group_by(journal,replicated1_clean) %>% filter(!is.na(journal)) %>% summarize(n=n()) %>% spread(replicated1_clean,n)
# the last entry is for NA
names(table2)[length(names(table2))] <- "NA"
func <- function(z) if (is.numeric(z)) sum(z,na.rm=TRUE) else ''
sumrow <- as.data.frame(lapply(table2, func))
sumrow[1] <- "Total"
names(sumrow)[length(sumrow)] <- "NA"
table2 <- bind_rows(table2,sumrow)  %>% mutate(Sum = sum(no,partially,yes,`NA`,na.rm = TRUE))
table2 <- head(table2,n=2)
write.csv(table2,file.path(TexIncludes,"journal_by_replicated.csv"),quote = FALSE,row.names = FALSE)
knitr::kable(table2)

```

Some quality diagnostics:
```{r qa1,results='asis'}
knitr::kable(repllist4 %>% mutate(flag_issue = as.numeric(is.na(`Main Issue`))) %>% filter(!is.na(journal)) %>%  group_by(flag_issue,replicated_clean) %>% summarise(n=n())  %>% spread(flag_issue,n),caption = "Presence of notes (Main Issue)")

```

## Replicators

Overall, there were `r nrow(table(repllist4$Replicator))` Replicators.

## Software

```{r}
entry_merge <- merge(entryQ,bibinfo.df,by="DOI",all.x= TRUE)
entry_merge_prog <- entry_merge %>%
  select(journal,ProgramFormat,year) %>%
  mutate(Stata = grepl("stata", tolower(ProgramFormat)),
         Matlab = grepl("matlab", tolower(ProgramFormat)),
         R = grepl(", r", tolower(ProgramFormat)) | tolower(ProgramFormat) %in% c("r"),
         SAS = grepl("sas", tolower(ProgramFormat)),
         Fortran = grepl("fortran", tolower(ProgramFormat)),
         Mathematica = grepl("mathematica", tolower(ProgramFormat)),
         SPSS = grepl("spss", tolower(ProgramFormat)),
         Eviews = grepl("eviews", tolower(ProgramFormat)),
         Excel = grepl("excel", tolower(ProgramFormat)),
         `Not Reported` = is.na(ProgramFormat))

# Make prog table
tab_prog <- entry_merge_prog %>% group_by(journal) %>%
  summarize(Stata = sum(Stata),
            Matlab = sum(Matlab),
            R = sum(R),
            SAS = sum(SAS),
            Fortran = sum(Fortran),
            Mathematica = sum(Mathematica),
            SPSS = sum(SPSS),
            Eviews = sum(Eviews),
            Excel = sum(Excel),
            `Not Reported` = sum(`Not Reported`)) %>% 
			mutate(Total = rowSums(select(.,-journal))) 
tab_prog_pct <- tab_prog 
tab_prog_pct[,-(1:1)] <- round(sweep(tab_prog[,-(1:1)],1,tab_prog$Total, "/")*100,2)

write.csv(tab_prog,file.path(TexIncludes,"software_by_journal.csv"),quote = FALSE,row.names = FALSE)
write.csv(tab_prog_pct,file.path(TexIncludes,"software_by_journal_pct.csv"),quote = FALSE,row.names = FALSE)
knitr::kable(tab_prog_pct)

# Define data format variable
entry_merge_data <- entry_merge %>%
  select(journal,OnlineDataFormat1,ProgramFormat,year) %>%
  mutate(Stata = grepl("stata", tolower(OnlineDataFormat1)),
         Matlab = grepl("matlab", tolower(OnlineDataFormat1)),
         R = grepl(", r", tolower(OnlineDataFormat1)) | tolower(ProgramFormat) %in% c("r"),
         Fortran = grepl("fortran", tolower(OnlineDataFormat1)),
         SPSS = grepl("spss", tolower(OnlineDataFormat1)),
         Excel = grepl("excel", tolower(OnlineDataFormat1)),
         CSV = grepl("csv", tolower(OnlineDataFormat1)),
         txt = grepl("txt", tolower(OnlineDataFormat1)),
         `Not Reported` = is.na(OnlineDataFormat1))

# Make data table
tab_data <- entry_merge_data %>% group_by(journal) %>%
  summarize(Stata = sum(Stata),
            Matlab = sum(Matlab),
            RDS = sum(R),
            Fortran = sum(Fortran),
            SPSS = sum(SPSS),
            Excel = sum(Excel),
            CSV = sum(CSV),
            txt = sum(txt),
            `Not Reported` = sum(`Not Reported`))  %>% 
			mutate(Total = rowSums(select(.,-journal))) 
tab_data_pct <- tab_data 
tab_data_pct[,-(1:1)] <- round(sweep(tab_data[,-(1:1)],1,tab_data$Total, "/")*100,2)

write.csv(tab_data,file.path(TexIncludes,"dataformat_by_journal.csv"),quote = FALSE,row.names = FALSE)
write.csv(tab_data_pct,file.path(TexIncludes,"dataformat_by_journal_pct.csv"),quote = FALSE,row.names = FALSE)
knitr::kable(tab_data_pct)



```

## NOT RUN YET


The final program produces the tables and figures. 

```{r analytics,eval=FALSE}
#source(file.path(programs,"05_analytics.R"),echo = TRUE)
```
